MINOS Handover Plots

### 2023-12-05 minos/validation/handovers.Rmd
LOTS of work on hourly_wage module to ensure living wage intervention is fully dynamic. Needs more work but its at a reasonable point. Some changes include: updated environment file to add missing R packages; small changes to transition estimation scripts to fix small issues; updated the hourly_wage module; improved the transitions Makefile to make it more clear which targets are for which runs; more I cant remember right now

# now a version limited to 0-100
spag <- spag %>%
  filter(hourly_wage <= 100)
spaghetti_plot(spag, 'hourly_wage',
               save = shall.we.save,
               save.path = save.path)

>>>>

# now a version limited to 0-100
spag <- spag %>%
  filter(hourly_wage <= 300)
spaghetti_plot(spag, 'hourly_wage',
               save = shall.we.save,
               save.path = save.path)
